---
title: "ddPCR_MS_SupplementalCode"
output: html_document
date: "2024-11-13"
---
Hello! Welcome to the paper for the ddPCR primers to identify (and quantify!) Schistocephalus in copepods. 

This is the code for the #Supplementary Material#.

#Libraries
```{r Let's load some libraries!}
#Libraries
library(ggplot2)
library(tidyverse)
library(dplyr)
library(readr)
library(forcats)
library(ggrepel)
library(ggpubr)
```

Set theme for ggplot
```{r Themes}
#Theme set
theme_set(  theme(legend.position = "none",
                  strip.background = element_rect(fill = "White"),
                  panel.background = element_rect(fill = "white",
                                                  colour = "black"), 
                  panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(), 
                  text = element_text(size = 14)))
```

#Let's load some data!
This includes one ddPCR run that looks at probe-primer specificity for both copepods (Cyclopoids/Calanoids) and Schistocephalus (solids/pungitii/cotti) across a temperature gradient.

```{r Loading the data}
specificity <- read_csv("SupplementaryMaterials_ddPCR_2025.csv") 

#####################
##Copepods Wells ###
#####################
#Here we can select a couple of specific wells to show that the probe-primers do not amplify Calanoids.
cyclo <- read_csv("Cyclpoid_Example.csv")
cyclo$Genus <- as.factor("Cyclopoida")

cala <- read_csv("Calanoid_Example.csv")
cala$Genus <- as.factor("Calanoida")

cope_compare<- rbind(cyclo, cala)


#####################
##Worm Wells ###
#####################
solidus <- read_csv("Solidus_Example.csv")
solidus$Species <- as.factor("S. solidus")

cotti <- read_csv("Cotti_Example.csv")
cotti$Species <- as.factor("S. cotti")

pungitii <- read_csv("Pungitii_Example.csv")
pungitii$Species <- as.factor("S. pungitii")

worm_compare<- rbind(solidus, pungitii, cotti)

```

#Wrangling data
```{rProbePrimer Specificity}
copes <- specificity %>%
  filter(str_detect(Sample, "calanoid|cyclopoid"), 
         Target == "HEX") #HEX dye for copepods

worms <- specificity %>%
  filter(str_detect(Sample, "solidus|cotti|pungitii"), 
         Target == "FAM") #FAM dye for helminths
```

#Imaging 
```{r ggplot comparison}

cope_compare %>%
  ggplot(aes(x = Genus)) +
  geom_hline(yintercept = 2000, linetype = "dashed", colour = "grey")+
  #Copepods (Black)
  geom_jitter(width = 0.1, height = 0,aes(y = `Ch2 Amplitude`), 
              fill = "grey",
              colour = "black", 
              alpha = 0.1, shape = 21) +
    labs(y = expression("Amplitude of fluorescence"))


worm_compare %>%
  ggplot(aes(x = Species)) +
  geom_hline(yintercept = 5500, linetype = "dashed", colour = "grey")+
  #Copepods (Black)
  geom_jitter(width = 0.1, height = 0,aes(y = `Ch1 Amplitude`), 
              fill = "#448F30",
              colour = "#448F30", 
              alpha = 0.1, shape = 21) +
    labs(y = expression("Amplitude of fluorescence"))

```


